\documentclass[a4paper, 12pt]{letter}
%\usepackage[left=1in,right=1in]{geometry}
\usepackage[left=1.5in, right=1.5in,top=1in]{geometry}
\name{FirstName LastName }
\address{Address
         }
%\date{today}
\begin{document}
\begin{letter}{ 
}



\opening{To whom it may concern,}
It is a pleasure to write this letter for XYZ. Last fall XYZ took the Introduction to Statistics in Biology of University of ABC and
I was the instructor of this online course. Since it's the only time that I have crossed path with XYZ, I'll focus on commenting on her performance in that course.

First I want to emphasize that it was not an easy course and many students struggled. One reason for this was because of its online format. There was no lecture, so students mainly need to teach themselves. They had to read the textbook and recommended readings to master various statistical concepts, models and methods which were completely new to most of them. I myself have been through graduate school and obtained a Ph.D degree in Statistics. It is my belief that self-motivation and self-learning ability are vitally important for the success of a graduate student. I'm glad to say XYZ excelled in this course and showed that she possesses such qualities. 

The workload of that course was kind of heavy. Each student was required to write an essay on population and sampling in a short time. 
XYZ got the highest score and demonstrated good writing style and solid understanding of the statistical concepts involved. The course also had several problem-solving assignments in which XYZ again scored high marks. 
There was one team project. Students were divided into teams of 5 or 6. Each team needed to complete a presentation about application of statistics in biology.
XYZ's team did a good job and her teammates gave her very positive comments. More ever, she has been very active in the course forum and often asked insightful questions and helped fellow students resolve various issues. 

I must admit that I don't know XYZ personally. But from what I have seen in that course, 
I believe she's a hard working, highly motivated student who has good potential to do excellent research. Hence I recommend her  to your program without any reservation.

If you have any question, please feel free to contact me.

Thank you very much!
\closing{Sincerely,}
\end{letter}
\signature{Anhua Lin}
\end{document}
